
\section{Contribution}

In this project, I have:

\begin{itemize}
    \item Proposed a novel assertion-based debugging framework for LLM-generated code, which enhances the reliability and correctness of synthesized code.
    \item Designed a multi-agent architecture that incorporates assertion-guided strategies, enabling efficient bug detection and localization during runtime.
    \item Implemented a multi-agent system that includes a divide-and-conquer agent for problem decomposition, programmer agents for code generation with assertions, and a debugger agent for iterative analysis of assertion failures.
    \item Conducted experiments on the HumanEvalPlus benchmark to evaluate the effectiveness of our framework.
\end{itemize}

\section{Conclusion and Future Directions}


In this project, I proposed an assertion-based debugging framework that enhances the reliability and correctness of LLM-generated code. By leveraging a multi-agent architecture, I demonstrated how assertion-guided strategies can improve bug detection and localization during runtime. Our experimental results on the HumanEvalPlus benchmark showed a significant performance gain, highlighting the effectiveness of our approach.

However, our project is not complete because of the limited time and resources. The experimental results are only conducted on the HumanEvalPlus benchmark, and even though it has been shown to have a lot randomness, I don't have the resourcaes to test it repeatedly. In the future, I plan to extend our framework to other benchmarks such as MBPPPlus\cite{evalplus} and MHPP\cite{MHPP}. I also aim to explore the integration of assertion-based debugging with other self-debugging and multi-agent collaboration techniques to further enhance the robustness and efficiency of program synthesis.

\section{LLM Usage Acknowledgements}

I have used ChatGPT and Github Copilot to complete this term paper. Here are the links to my conversations. I also put my usage of Github Copilot in the same place:

\begin{itemize}
    \item \href{https://chatgpt.com/share/67fc7d4f-f974-8006-9237-2e2d4fe3eadb}{https://chatgpt.com/share/67fc7d4f-f974-8006-9237-2e2d4fe3eadb}
    \item \href{https://chatgpt.com/share/67fc7cd5-d450-8006-af1c-df824848c97f}{https://chatgpt.com/share/67fc7cd5-d450-8006-af1c-df824848c97f}
    \item \href{https://chatgpt.com/share/67fc7d5d-ea08-8006-a7fc-adf3aa387d13}{https://chatgpt.com/share/67fc7d5d-ea08-8006-a7fc-adf3aa387d13}
    \item \href{https://chatgpt.com/share/67cb68ef-9168-8006-8ad2-7fe15217ad08}{https://chatgpt.com/share/67cb68ef-9168-8006-8ad2-7fe15217ad08}
    \item \href{https://chatgpt.com/share/67cb6920-14c8-8006-937e-e3a9c38144a7}{https://chatgpt.com/share/67cb6920-14c8-8006-937e-e3a9c38144a7}
\end{itemize}

However, I failed to track some of the text generated by Github Copilot, which I borrowed from the Checkpoint 2 writeup. It is mainly in Section 1 \& 2.
